Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study

### 2020-08-19 paper/aimusic2020/paper.tex
Minor fixes and formatting
Small change

\subsection{From orchestration to classification}

@@

\subsection{Classification results}

@@

Fig. \ref{best_acc_cnn} and Fig. \ref{best_acc_resnet} show the maximum accuracy computed using the function $f$ from Eqn. \ref{eval}. For ResNet, the variance in accuracy is much smaller until $N$ reaches 5, at which point it becomes similar to the CNN. The results on both figures show consistency on the relative accuracy of instruments, which was for us the first step towards the validation of this method. Flute, Trombone and Trumpet yield the worst results for both models.

@@

\section{Orchestration experiments}
\label{sec:orchestration}

After training the neural models for classification, we finally tested them for the task of target-based computer-assisted orchestration. For this purpose, we decided to use the models trained on combinations of 10 instruments, namely French Horn, Oboe, Violin, Viola, Cello, Flute, Trombone, Bassoon, Trumpet, and Clarinet. Each class, in this model, represents an instrument-pitch pair.

>>>>

\subsection{From Orchestration to Classification}

@@

\subsection{Classification Results}

@@

Fig. \ref{best_acc_cnn} and Fig. \ref{best_acc_resnet} show the maximum test accuracy for each model. For ResNet, the variance in accuracy is much smaller until $N$ reaches 5, at which point it becomes similar to the CNN. The results on both figures show consistency on the relative accuracy of instruments, which was for us the first step towards the validation of this method. Flute, Trombone and Trumpet yield the worst results for both models.

@@

\section{Orchestration Experiments}
\label{sec:orchestration}

After training the neural models for classification, we finally tested them for the task of target-based computer-assisted orchestration. For this purpose, we decided to use the models trained on combinations of 10 instruments: French Horn, Oboe, Violin, Viola, Cello, Flute, Trombone, Bassoon, Trumpet, and Clarinet. Each class, in this model, represents an instrument-pitch pair.
